---
title: "The Ultimate Regression App"
author: "Erik Hirschfeld"
date: "13 September 2019"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

dta <- data.frame(
  matrix(c(21, 110, 2.62, 21, 110, 2.875, 22.8,93,2.32, 21.4,110,3.215,
           18.7,175,3.44, 18.1,105,3.46, 14.3,245,3.57, 24.4,62,3.19,
           22.8,95,3.15, 19.2,123,3.44, 17.8,123,3.44, 16.4,180,4.07, 
           17.3,180,3.73, 15.2,180,3.78, 10.4,205,5.25,10.4,215,5.424,
           14.7,230,5.345,32.4,66,2.2,30.4,52,1.615,33.9,65,1.835,
           21.5,97,2.465,15.5,150,3.52,15.2,150,3.435,13.3,245,3.84,
           19.2,175,3.845,27.3,66,1.935,26,91,2.14,30.4,113,1.513,
           15.8,264,3.17,19.7,175,2.77,15,335,3.57,21.4,109,2.78), ncol = 3, byrow = TRUE))
names(dta) <- c("dep", "pred1", "pred2")
```

## The Ultimate Regression App

The new and ultimate regression app helps people without programming knowledge to easily perform regression !!!

## Functionality

The user just uploads a CSV file, afterwards the user can select in a user friendly interface which variable to model, if there is a weight variable and which variables to use in the regression as predictors.

## Result 1: Data Summary

To check the uploaded data the data summary will be displayed:
```{r, echo = FALSE}
summary(dta)
```

## Result 2: Model Results
The model summary is directly displayed in the browser:
\tiny
```{r, echo = FALSE}
summary(lm(dep ~ pred1 + pred2, data = dta))
```

## Thank You

Don't miss this opportunity and invest in the ultimate app !!!




